Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-01 ms.qmd
small adjustments

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```

#### Plots of $I^2$ for multi-level models
```{r, fig-s3}
#| label: fig-s3
#| fig-cap: I2 estimates
#| fig-align: center

>>>>

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```
install.packages("flextable")
#### Plots of $I^2$ for multi-level models
```{r, fig-s3}
#| label: fig-s3
#| fig-cap: I2 estimates
#| fig-align: center
